Energy and exergy analysis of a cruise ship

### 2017-07-05 Manuscript/Manuscript.tex
Other updates to the py files...I am getting bored of writing this :-)

Figure XX represents the distribution and the evolution over the year of the ambient air and sea water temperature. The relatively low temperatures that are experienced by the case study ship during its operations suggest that heating demand can be expected to be higher than cooling demand. On the other hand, the fact that, in summer, air temperatures reach up to 26 degrees Celsius justify the existence of an HVAC unit that can also operate in cooling mode.

Figure XX represents the distribution of the ship speed, both in terms of statistical distribution and in terms of a reference 24h period. The ship operates almost for the entire year according to a fix schedule.

@@

@@

>>>>

Figure \ref{fig:Tsea_vs_time} represents the distribution and the evolution over the year of the ambient air and sea water temperature. The relatively low temperatures that are experienced by the case study ship during its operations suggest that heating demand can be expected to be higher than cooling demand. On the other hand, the fact that, in summer, air temperatures reach up to 26 degrees Celsius justify the existence of an HVAC unit that can also operate in cooling mode.

The corresponding ditributions are presented in Figure \ref{fig:Tsea_hist}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Tsea_vs_time}
	\caption{Yearly evolution of sea water and ambient air temperatures. Landsort, 2014}
	\label{fig:Tsea_vs_time}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/Tsea_hist}
	\caption{Yearly distribution of sea water and ambient air temperatures. Landsort, 2014}
	\label{fig:Tsea_hist}
\end{figure}

Figure \ref{fig:vship_hist} represents the distribution of the ship speed, both in terms of statistical distribution and in terms of a reference 24h period. The ship operates almost for the entire year according to a fix schedule.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{Figures/vship_hist}
	\caption{Yearly distribution of ship speed}
	\label{fig:vship_hist}
\end{figure}

@@

In Figure \ref{fig:Heat_vs_time} the heat generated by different hot utilities, as estimated by the model, is shown. It should be noticed that, while the heat generated by the HRSGs represents a rather accurate estimation, all other data series (auxiliary boilers, HTHR) are the consequence of rather strong assumptions.

The figure also shows the operation of validation of the assumptions by comparison of the measured values for the boilers fuel consumption (here translated into an energy-per-day basis to ease the comparison). It should be noted that, although the absolute value is still quite different compared to the calculated one (mean error is 255\%, minimum 3\%), there is evidence that the order of magnitude is similar, and that some trends are followed

\begin{figure}
	\centering
	\includegraphics[width=0.99\linewidth]{Figures/Heat_vs_time}
	\caption{Yearly evolution of heat generated by different sources. "Measured" and "Calculated" relate to the auxiliary oil-fired boilers}
	\label{fig:Heat_vs_time}
\end{figure}
